Visual Analysis of Ligand Trajectories in Molecular Dynamics

### 2018-09-28 paper.tex
Added authors

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Roy G. Biv\thanks{e-mail: roy.g.biv@aol.com}\\ %
        \scriptsize Starbucks Research %
\and Ed Grimley\thanks{e-mail: ed.grimley@aol.com}\\ %
     \scriptsize Grimley Widgets, Inc. %
\and Martha Stewart\thanks{e-mail: martha.stewart@marthastewart.com}\\ %
     \parbox{1.4in}{\scriptsize \centering Martha Stewart Enterprises \\ Microsoft Research}}

>>>>

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Adam Jur\v{c}\'{i}k\thanks{e-mail: xjurc@fi.muni.cz}\\ %
        \scriptsize Masaryk University %
\and Katar\'{i}na Furmanov\'{a}\\ %
     \scriptsize Masaryk University %
\and Jan By\v{s}ka\\ %
     \parbox{1.4in}{\scriptsize \centering University of Bergen \\ Masaryk University} %
\and Vojt\v{e}ch Von\'{a}sek\\ %
     \scriptsize Czech Technical University %
\vspace{\baselineskip} %
\and Ond\v{r}ej V\'{a}vra\\ %
     \scriptsize Masaryk University %
\and Pavol Ulbrich\\ %
     \scriptsize Masaryk University
\and Helwig Hauser\\ %
     \scriptsize University of Bergen %
\and Barbora Kozl\'{i}kov\'{a}\\ %
     \scriptsize Masaryk University}
